Stochastic Approximation Monte Carlo with a Dynamic Update Factor

### 2019-11-12 papers/histogram/sad.tex
plot a few more C_V (which still need refining) and work more on LJ31 text.

Poulain \emph{et al.} found \cite{poulain2006performances}

The heat capacity changes significantly even at these low temperatures
when the size of the cavity is increased.  We use a 2.5 cavity because
``everyone else'' does.  For purposes of testing the convergence of
the algorithm, we don't need to solve for the true heat capacity.
Furthermore, the heat capacity at fixed volume is not the most
meaningful quantity to predict for a cluster.

>>>>

Poulain \emph{et al.} found very poor convergence for a variety of
modified WL methods on the LJ31
cluster~\cite{poulain2006performances}.  Sadly, they don't mention the
energy range or bin size that was used in their simulation, so their
results cannot be reproduced.  They do mention that they use 1000
energy bins, which if they used an energy range of
$[-133.58\epsilon,0]$ would correspond to a bin size of $\Delta
E\approx 0.13\epsilon$, which we find to be too large to accurately
predict the heat capacity peak at $0.03\epsilon/k_B$.

The heat capacity changes significantly even at these low temperatures
when the size of the cavity is increased.  We use a 2.5 cavity because
``everyone else'' does~\cite{poulain2006performances}.  For purposes
of testing the convergence of the algorithm, we don't need to solve
for the true heat capacity.  Furthermore, the heat capacity at fixed
volume is not the most meaningful quantity to predict for a cluster.
